\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-11-01 OaklandSubmission/ex.tex
nits

Figure~\ref{fig:toolchain} shows an overview of the \tool
toolchain. We give a brief overview of each of these phases below.

\subsubsection*{Source language}
Consider the example $w^Tx >b$ from Section~\ref{sec:intro}, where
$w$ and $b$ constitute the server's input (a classifier) and $x$ is
the client's input vector. Figure~\ref{fig:ex-sml} shows the \tool code
for this example. The code first reads the server's (resp. client's) input using
 \ls{input1} (resp. \ls{input2}). It then uses a
\ls{for} loop to compute \ls{acc}, the inner product of \ls{w} and
\ls{x}. Finally, the code outputs the result of comparing \ls{acc}
with \ls{b} only to the client using \ls{output2}.

@@

\subsubsection*{\tool compiler}
\tool compiler takes as input a source program and produces a C++
program as output. Figure~\ref{fig:ex-aby} shows the output code\footnote{This is also how a program written directly in
  ABY would look like.} for
the example in Figure~\ref{fig:ex-sml}. The output program
contains party-specific code for inputs and outputs
(\ls{role == SERVER} and \ls{role == CLIENT}), and common code for the
computation.

The compiler splits the input
program into \emph{public} and \emph{secret} components. The public
components translate into regular C++ code, while the secret
components translate into API calls into our \mpc back-end
(ABY). For example, in Figure~\ref{fig:ex-sml}, the \tool
compiler realizes that the array index \ls{i} in the inner product loop
is public, and hence the access locations need not be hidden.
Therefore, it compiles the \ls{for}~loop into a C++
\ls{for}~loop that will be executed in-clear
(line~\ref{line:dotproductloop}).

Within the secret components, the \tool compiler is ``cryptographic
cost-aware'', and appropriately picks either arithmetic or boolean
circuit representations for different sub-components. For example,
the compiler realizes that the inner product computation is more
efficient in the arithmetic representation, and therefore it builds
the corresponding circuit using the arithmetic circuit builder
\ls{acirc} (lines~\ref{line:dotmulgate} and~\ref{line:dotaddgate}). On
the other hand, since the comparison with \ls{b}, and the conditional
expression computation are more efficient in the boolean
representation, the \tool compiler uses the Yao circuit builder
\ls{ycirc} to build the corresponding circuits
(lines~\ref{line:condyaobegin} to~\ref{line:condyaoend}) (in our usage
of ABY, boolean is synonymous with Yao (Section~\ref{sec:impl})).

@@

$\mathtt{
if(role == CLIENT) \{\;\;\textbf{\color{blue}//only to the client}
}$
$\mathtt{
\;\;\;\;uint32\_t \_o = y\_out\rightarrow get\_clear\_value\langle uint32\_t \rangle();
}$
$\mathtt{
\}
}$
\end{lstlisting}
\caption{\tool compiler (partial) output for Figure~\ref{fig:ex-sml}}
\label{fig:ex-aby}
\end{figure}

@@

We can now concretely see the advantages of \tool. Unarguably, it is
easier for a developer to program and get right the code in
Figure~\ref{fig:ex-sml}, rather than the code in
Figure~\ref{fig:ex-aby}.
% (as we mentioned in Section~\ref{sec:intro},
%other high-level languages are limited in their use of a single,
%arithmetic or boolean, crypto back-end). 
\tool also enables the
programmer to easily modify their code, while the compiler takes care
of efficiency. For example, consider in Figure~\ref{fig:ex-sml} a
change from multiplication to bitwise-or in the \ls{for} loop. It
turns out that once that's the case, it is more efficient to do both
the addition and bitwise-or using boolean circuits (if the addition is
still done using arithmetic, the conversion cost starts to take
over). In \tool, the programmer simply needs to change one operator in
the source code, and the compiler generates efficient code that uses
boolean addition. Whereas, if the programmer was writing ABY
code, she either has to sacrifice performance, or she would have to
revisit many parts of the circuit and change them.

>>>>

\figureref{toolchain} shows an overview of the \tool
toolchain. We give a brief overview of each of these phases below.

\subsubsection*{Source language}
Consider the example $w^Tx >b$ from \sectionref{intro}, where
$w$ and $b$ constitute the server's input (a classifier) and $x$ is
the client's input vector. \figureref{ex-sml} shows the \tool code
for this example. The code first reads the server's (resp. client's) input using
 \ls{input1} (resp. \ls{input2}). It then uses a
\ls{for} loop to compute \ls{acc}, the inner product of \ls{w} and
\ls{x}. Finally, the code outputs the result of comparing \ls{acc}
with \ls{b} only to the client using \ls{output2}.

@@

\subsubsection*{\tool compiler}
\tool compiler takes as input a source program and produces a C++
program as output. \figureref{ex-aby} shows the output code\footnote{This is also how a program written directly in
  ABY would look like.} for
the example in \figureref{ex-sml}. The output program
contains party-specific code for inputs and outputs
(\ls{role == SERVER} and \ls{role == CLIENT}), and common code for the
computation.

The compiler splits the input
program into \emph{public} and \emph{secret} components. The public
components translate into regular C++ code, while the secret
components translate into API calls into our \mpc back-end
(ABY). For example, in \figureref{ex-sml}, the \tool
compiler realizes that the array index \ls{i} in the inner product loop
is public, and hence the access locations need not be hidden.
Therefore, it compiles the \ls{for}~loop into a C++
\ls{for}~loop that will be executed in-clear
(line~\ref{line:dotproductloop}).

Within the secret components, the \tool compiler is ``cryptographic
cost-aware'', and appropriately picks either arithmetic or boolean
circuit representations for different sub-components. For example,
the compiler realizes that the inner product computation is more
efficient in the arithmetic representation, and therefore it builds
the corresponding circuit using the arithmetic circuit builder
\ls{acirc} (lines~\ref{line:dotmulgate} and~\ref{line:dotaddgate}). On
the other hand, since the comparison with \ls{b}, and the conditional
expression computation are more efficient in the boolean
representation, the \tool compiler uses the Yao circuit builder
\ls{ycirc} to build the corresponding circuits
(lines~\ref{line:condyaobegin} to~\ref{line:condyaoend}) (in our usage
of ABY, boolean is synonymous with Yao, we elaborate in \sectionref{impl}).

@@

$\mathtt{
if(role == CLIENT) \{\;\;\textbf{\color{blue}//only to the client}
}$
$\mathtt{
\;\;\;\;uint32\_t \_o = y\_out\rightarrow get\_clear\_value\langle uint32\_t \rangle();
}$
$\mathtt{
\}
}$
\end{lstlisting}
\caption{\tool compiler (partial) output for \figureref{ex-sml}}
\label{fig:ex-aby}
\end{figure}

@@

We can now concretely see the advantages of \tool. Unarguably, it is
easier for a developer to program and get right the code in
\figureref{ex-sml}, rather than the code in
\figureref{ex-aby}.
% (as we mentioned in Section~\ref{sec:intro},
%other high-level languages are limited in their use of a single,
%arithmetic or boolean, crypto back-end). 
\tool also enables the
programmer to easily modify their code, while the compiler takes care
of efficiency. For example, consider in \figureref{ex-sml} a
change from multiplication to bitwise-or in the \ls{for} loop. It
turns out that once that's the case, it is more efficient to do both
the addition and bitwise-or using boolean circuits (if the addition is
still done using arithmetic, the conversion cost starts to take
over). In \tool, the programmer simply needs to change one operator in
the source code, and the compiler generates efficient code that uses
boolean addition. Whereas, if the programmer was writing ABY
code, she either has to sacrifice performance, or she would have to
revisit many parts of the circuit and change them.

### 2017-11-01 OaklandSubmission/impl.tex
nits

We use an off-the-shelf solver
(SeaHorn~\cite{seahorn}) to bound check the array indices
($\models e < n$
in ({\sc {T-Read}}) and ({\sc{T-Write}})),
Figure~\ref{fig:compile}). We take the \tool source program and
translate it as an input to the solver. The solver takes less
than a minute on our largest benchmark to verify that all the array
accesses are in-bounds.

@@

The compilation rules of Figure~\ref{fig:compile} can introduce
repeated coercions from arithmetic to
boolean and vice versa.
Since \tool is aware of the cryptographic costs associated with these coercions,
it tries to minimize them using several optimizations.
For instance, if boolean shares of a variable are available in scope and the variable is involved in
an addition then \tool performs the addition in boolean rather than first coercing boolean to arithmetic
and then performing an arithmetic addition. However, multiplication is always performed in arithmetic
as the cost of a boolean multiplication is much higher than the cost of coercing from boolean to arithmetic, performing an arithmetic multiplication, and then coercing from arithmetic to boolean~\cite{aby}.
Other optimizations include the standard ``common subexpression elimination"
optimization~\cite{dragonbook}.
On each coercion, \tool memorizes the pair of arithmetic
share and boolean share involved in the coercion. 
\tool invalidates such pairs when the variables corresponding to the
shares are overwritten by assignments. 
In subsequent coercions, \tool  reuses valid pairs (if available)
instead of inserting code to recompute them afresh.

>>>>

We use an off-the-shelf solver
(SeaHorn~\cite{seahorn}) to bound check the array indices
($\models e < n$
in ({\sc {T-Read}}) and ({\sc{T-Write}}),
\figureref{compile}). We take the \tool source program and
translate it as an input to the solver. The solver takes less
than a minute on our largest benchmark to verify that all the array
accesses are in-bounds.

@@

The compilation rules of \figureref{compile} can introduce
repeated coercions from arithmetic to
boolean and vice versa.
Since \tool is aware of the cryptographic costs associated with these coercions,
it tries to minimize them using several optimizations.
For instance, if boolean shares of a variable are available in scope and the variable is involved in
an addition then \tool performs the addition in boolean rather than first coercing boolean to arithmetic
and then performing an arithmetic addition. However, multiplication is always performed in arithmetic
as the cost of a boolean multiplication is much higher than the cost of coercing from boolean to arithmetic, performing an arithmetic multiplication, and then coercing from arithmetic to boolean~\cite{aby}.
Other optimizations include the standard ``common subexpression elimination"
optimization~\cite{dragonbook}.
On each coercion, \tool memorizes the pair of arithmetic
share and boolean share involved in the coercion. 
\tool invalidates such pairs when the variables corresponding to the
shares are overwritten by assignments. 
In subsequent coercions, \tool  reuses valid pairs (if available)
instead of inserting code to recompute them afresh.
